Titeln på avhandlingens språk

### 2022-10-04 model.tex
results of synthetic setup

\begin{figure*}
    \centering
    \includegraphics[width=.9\textwidth]{figs/model_comp_controlled_ttf.png}
    \begin{tabular}{ll >{\columncolor[HTML]{EAEAEA}}r >{\columncolor[HTML]{EAEAEA}}r rr}
    \toprule
    {} & {} & \multicolumn{2}{>{\columncolor[HTML]{EAEAEA}}c}{\ac{TTF} \( = \) \SI{0}{\second}} & \multicolumn{2}{c}{\ac{TTF} \( = \) \SI{5}{\second}} \\
    {Model} & {Neuroticism} & {Total Duration} & {Diff.\ w.r.t.\ fitted-naive} & {Total Duration} & {Diff.\ w.r.t.\ fitted-naive} \\
    \midrule
    fitted-naive & n/a & \SI{576.74}{\second} & & \SI{1084.57}{\second} & \\
    \multirow[c]{2}{*}{empirical} & low & \SI{511.18}{\second} & \SI{-11.37}{\percent} & \SI{1083.40}{\second} & \SI{-0.11}{\percent} \\
    & high & \SI{533.29}{\second} & \SI{-7.53}{\percent} & \SI{1245.46}{\second} & +\SI{14.84}{\percent} \\
    \multirow[c]{2}{*}{theoretical} & low & \SI{504.73}{\second} & \SI{-12.49}{\percent} & \SI{1080.16}{\second} & \SI{-0.41}{\percent} \\
    & high & \SI{539.00}{\second} & \SI{-6.54}{\percent} & \SI{1225.68}{\second} & +\SI{13.01}{\percent} \\
    \bottomrule
    \end{tabular}
    \caption{
        Comparison of the total duration of \num{100}-step tasks for different models in the controlled \ac{TTF} setup.
        The results are separated for clarity, with the top plot showing the results for the realistic models, and the bottom one for the reference models.
    }\label{fig:ctrlttf}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=.9\textwidth]{figs/model_comp_controlled_ttf.png}
    \begin{tabular}{ll >{\columncolor[HTML]{EAEAEA}}r >{\columncolor[HTML]{EAEAEA}}r rr}
    \toprule
    {} & {} & \multicolumn{2}{>{\columncolor[HTML]{EAEAEA}}c}{\ac{TTF} \( = \) \SI{0}{\second}} & \multicolumn{2}{c}{\ac{TTF} \( = \) \SI{5}{\second}} \\
    {Model} & {Neuroticism} & {Total Duration} & {Diff.\ w.r.t.\ fitted-naive} & {Total Duration} & {Diff.\ w.r.t.\ fitted-naive} \\
    \midrule
    fitted-naive & n/a & \SI{576.74}{\second} & & \SI{1084.57}{\second} & \\
    \multirow[c]{2}{*}{empirical} & low & \SI{511.18}{\second} & \SI{-11.37}{\percent} & \SI{1083.40}{\second} & \SI{-0.11}{\percent} \\
    & high & \SI{533.29}{\second} & \SI{-7.53}{\percent} & \SI{1245.46}{\second} & +\SI{14.84}{\percent} \\
    \multirow[c]{2}{*}{theoretical} & low & \SI{504.73}{\second} & \SI{-12.49}{\percent} & \SI{1080.16}{\second} & \SI{-0.41}{\percent} \\
    & high & \SI{539.00}{\second} & \SI{-6.54}{\percent} & \SI{1225.68}{\second} & +\SI{13.01}{\percent} \\
    \bottomrule
    \end{tabular}
    \caption{
        Comparison of the total duration of \num{100}-step tasks for different models in the controlled \ac{TTF} setup.
        The results are separated for clarity, with the left plot showing the results for the realistic models, and the right the reference models.
        The table shows a detailed breakdown of durations for the fitted-naive, empirical, and theoretical models at the lowest and highest \acp{TTF}, as well as relative differences with respect to the corresponding fitted-naive baseline for each case.
    }\label{fig:ctrlttf}
\end{figure*}
